---
title: "DMC Project: Employment statistics of graduate students"
author: "Lou Delattre and Yufeng Jiang"
format: 
  html: default 
  wordcount-pdf: default 
execute: 
  echo: false
  warning: false
---

```{r}
here::i_am("DM-project-Employment-statistics-of-graduate-student.Rproj")
library(here)
library(vroom)
library(ggplot2)
library(dplyr)
library(tidyr)
library(purrr)
library(knitr)
theme_set(theme_bw())
```

Github repository: <https://github.com/Mapleyf0911/DM-project-Employment-statistics-of-graduate-student.git>

## Goal of our research

We will define the goals of our quantitative analysis. Data on the insertion rate and different measures of wages allow us to compute and make comparisons between sectors, and to emit hypotheses on correlations between some of our variables at various levels. Expressing these hypotheses, we obtain the following questions:

-   Which fields/specializations lead to the highest wages, have the highest insertion rate, or have the highest level of stable employment? This will be the focus of our analysis. We can compute the mean wage/rate for each field and make comparisons.

-   Is the university that one goes to a significant factor to explain wages? We could take one field/specialization taught at different universities, focus on these observations to make a (simple) regression, and try to determine the significance of the "university" factor.

-   How do the wages of these graduates compare to the average national/regional salaries? How do they compare to the average of their respective fields? Using the results of the first question and data from the additional data set, various plot representations could be meaningful.

-   Are there significant differences between observations made 18 months after graduating and observations made 30 months after graduating? It will be necessary to separate the programs where we have 18-month observations, those with 30-month observations, and those with both, and isolate this last category.

-   Do some specializations require to leave the region of the "académie" where the master's degree was done? It could show the concentration of certain industries at national level. 

-   Do some specializations attract more women/scholarship students? There are already studies on the type of profile each field is more likely to attract, thus we can try to find the same results with our data set.

We do not have a unique research question, as it would not allow us to do enough testing at our level, given our data set. However, all of the above-mentioned questions go in the same direction: what can be inferred from our data sets about the situation of graduate students? This will certainly be insufficient to make any real conclusions, nonetheless this may help define guidelines for a bigger project.

## The datasets

### Data import

We aim to analyze the employability, situation of employment and salary of graduate students, depending on their graduate program, university and "académie".

Here, we are using employment statistics from the professional insertion survey of Master students made by the Ministère de l'Enseignement Supérieur et de la Recherche. The survey focus on French graduate students who have completed their initial training ("formation initiale" in French) and have not continued or resumed their studies in the two years following their graduation. The survey shows the employment status at two key time points: 18 months and 30 months after their graduation.

#### Main dataset

```{r}
insertion_master <- vroom(here("data", "fr-esr-insertion_professionnelle-master-national.csv"))
```

|                        |                            |
|------------------------|----------------------------|
| Number of observations | `r NROW(insertion_master)` |
| Number of variables    | `r NCOL(insertion_master)` |

**Source:** <https://data.enseignementsup-recherche.gouv.fr/explore/embed/dataset/fr-esr-insertion_professionnelle-master/table/?disjunctive.academie&disjunctive.numero_de_l_etablissement&sort=-annee>

In this data set, each observation includes:

-   The year of the survey, the type of master's degree, the university number and the "académie" number and name;

-   The name of the university responsible of the degree, the field ("domaine") and subject ("discipline") of the graduate program;<br>

-   The number of responses and response rate;<br>

-   The percentage of women and scholarship students; <br>

-   The "insertion" rate (% of the graduates that are employed);<br>

-   The percentage of students that work full-time, in executive positions, and outside the region of their university;<br>

-   The median monthly net salary and the estimated gross annual salary of graduates that work full time;<br>

-   The regional unemployment rate; <br>

-   First and third quartiles regional net monthly salaries. <br>

#### Complementary data set

For comparison purposes, we found wage data in a report titled "Île-de-France accounts for half of the highest-paid private sector employees in France" of Insee. The data used for this report was collected by the Insee from two databases (Tous Salariés and Flores).<br>

The database Tous Salariés has all the information about employees. They use the administrative declaration submitted by employers. In the private sector, the annual salary salaries and the number of employees data are mainly derived from Nominative Social Declarations ("Déclarations sociales nominatives (DSN)" in French) and Annual Social Data Declaration ("Déclarations annuelles des données sociales (DADS)" in French). Employees in the agricultural sector, employees of private households, apprentices, and interns are excluded from this study.

The database (Flores 2018) covers all employers (civil service, private employers, including individual employers), with the exception of the employment activities of the Ministry of Armed Forces (France). This database can be used to describe salaried employment across all sectors.

From the data set, we have 2018 data on median/average salaries in the Île-de-France region and at national level, taking into account multiple variables such as sector, type of position and gender. We estimate there are enough sectors included in the file to classify all graduate programs.

Source: <https://data.enseignementsup-recherche.gouv.fr/explore/embed/dataset/fr-esr-insertion_professionnelle-master/table/?disjunctive.numero_de_l_etablissement&disjunctive.academie&sort=-salaire_net_median_des_emplois_a_temps_plein&refine.academie=Paris>

This data is presented in several tables. We simply split the file by each table and removed some textual explanatory information before importing the needed table into R.

We have:

-   the different deciles of net wages at the Île-de-France and national levels;

```{r}
Net_wage_EQTP <- vroom(here("data", "Figure_1_Distribution_of_Monthly_Net_Wages_in_Ile-de-France_and_France_EQTP.csv"))
```

-   the percentage of different types of earners in the Île-de-France regions;

```{r}
pct_high_income <- vroom(here("data", "Figure_2_Ile-de-France_Share_in_High_Incomes_High_Wealth_and_High_Wages.csv"))
```

-   the average net wages of each gender in different employment categories;

```{r}
wages_profession_gender <- vroom(here("data", "Figure_4_Average_Monthly_Net_Wages_EQTP_by_Socio-Professional_Category_and_Gender.csv"))
```

|                                         |                                         |
|-----------------------------------------|-----------------------------------------|
| Number of socio-professional categories | `r (NROW(wages_profession_gender)-2)/2` |
| National mean for men                   | `r wages_profession_gender[10,4]`       |
| National mean for women                 | `r wages_profession_gender[10,3]`       |
| IDF mean for men                        | `r wages_profession_gender[5,4]`        |
| IDF mean for women                      | `r wages_profession_gender[5,3]`        |

<small>**Note:** IDF (Île-de-France)</small>

#### Dataset joining

Here, we get the panel data "insertion_master_panel" by joining the wage data from the complementary data set to our main data set.

```{r}
Net_wage_EQTP_wide_regional_national <- Net_wage_EQTP |>
    pivot_wider(names_from = ...1, values_from = c(`ile-de-France`, France), 
              names_sep = " ") 
##
rows_to_fill <- nrow(insertion_master) - nrow(Net_wage_EQTP_wide_regional_national)
##
if (rows_to_fill > 0) {
  repeated_data <- map(1:rows_to_fill, ~ Net_wage_EQTP_wide_regional_national) |>
    bind_rows()
  Net_wage_EQTP_wide_regional_national <- bind_rows(Net_wage_EQTP_wide_regional_national, repeated_data)
}

insertion_master_panel <- cbind(insertion_master, Net_wage_EQTP_wide_regional_national)
```

### Data cleaning

In our main data set, there are 35 variables. Some of them might be superfluous or at least not relevant for our analysis.

-   "Etablissement actuel" (the 5th column) just gives the exact full name of the university, but in reality we know the corresponding university from the abbreviation, so this column is not very helpful to our research and can bu deleted.

-   "cle_ETAB" (the 33th column) could be obtained using more explicit columns. It is redundant.

-   "Id_Paysage" (the 35th column) is redundant. It has the same purpose as "Code de l'établissement".

-   "Taux d'emploi" (the 18th column) and "Taux d'emploi en France" (the 19th column) are missing a significant amount of values (17669 out of 19603 observations). We consider that "Taux d'insertion" is sufficient, as the difference between the employment rate and insertion rate may not be significant. According to the original source, the employment rate is computed including "inactives" (neither working nor in search of employment.) while the insertion rate does not include them.

Therefore, we can delete the 5th, 18th, 19th, 33th and 35th columns in the original dataset.

```{r}
insertion_master_panel <- insertion_master_panel |> select(-c(5, 18, 19, 33, 35))
```


However, some graduate programs have two observations (one after 18 months, one after 30 months). To perfectly identify each observation of each master program, we have to create another variable (or primary key).

-   The identifier is called "obs_ID" and is made of the concatenation of "Annee", "Numéro de l'établissement" and "cle_disc".

```{r}
## création clé 
insertion_master_panel <- insertion_master_panel |>
  mutate(obs_ID = paste(Annee,  `Numéro de l'établissement`, `cle_DISC`, sep = "_"))
```

In the "Remarque" column, there are five possible values for each observation:

1. Université ayant participé à l'enquête mais dont l'effectif est trop petit pour que les résultats soient jugés exploitables;
2. Université ayant participé à l'enquête mais dont le taux de réponse obtenu est insuffisant pour que les résultats soient jugés exploitables;
3. Université dont les résultats sont plus fragiles (taux de réponse inférieur à 50%);
4. Université n'ayant pas participé à l'enquête;
5. N/A (no comment).

Among all observations, only those where the "Remarque" column is either "Université dont les résultats sont plus fragiles (taux de réponse inférieur à 50%)" or "N/A" contain the necessary data for further analysis (e.g., graduate employment rates and salary levels). Therefore, we will retain only those observations that meet these two conditions.

Some of the observations are on gathered data from all degrees of the same discipline, by year. As they are on national data, they are not related to any "académie". We will keep them for analysis purposes but after removing them from the main data set. 

```{r}
## removing 
insertion_master_panel <- insertion_master_panel |> 
  filter(is.na(Remarque)| Remarque == "Université dont les résultats sont plus fragiles (taux de réponse inférieur à 50%)" )

## isolating aggregate observations 
aggregate_data <- insertion_master_panel |> 
  filter(is.na(Académie))

## removing aggregate observations from main dataset 
insertion_master_panel <- insertion_master_panel |> filter(!is.na(Académie))

```

In our data set "insertion_master_panel", many values are missing, due to absence of data ("nd" = non disponible) or unusable data ("ns" = "non significatif" and "fe" = "faible effectif"). Here, we examine how many missing values we have in each column, and address these missing values carefully before our analysis.

```{r}
selected_columns <- insertion_master_panel[, 14:32]

is_non_numeric <- function(x) {
  !is.numeric(suppressWarnings(as.numeric(as.character(x)))) | is.na(x)
}
non_numeric_counts <- sapply(selected_columns, function(column){
  sum(is_non_numeric(column))
})
  
kable(data.frame(non_numeric_counts))
```


```{r}
insertion_master_panel[] <- lapply(insertion_master_panel, function(x) ifelse(x == "ns", NA, x))
insertion_master_panel[] <- lapply(insertion_master_panel, function(x) ifelse(x == "nd", NA, x))
insertion_master_panel[] <- lapply(insertion_master_panel, function(x) ifelse(x == "fe", NA, x))
insertion_master_panel[] <- lapply(insertion_master_panel, function(x) ifelse(x == ".", NA, x))
```

To facilitate our future analysis, we convert some character-formatted data values into numeric format.

```{r}
cols_to_convert <- c(16:20, 23:29)
insertion_master_panel[, cols_to_convert] <- sapply(insertion_master_panel[, cols_to_convert], function(x){
  if (is.character(x)){
    as.numeric(ifelse(is.na(x), NA, x))
  } else {
    x
  }
})
```



## Data analysis


|   Categories   |                             Number                              |
|:---------------------:|:----------------------------------------------:|
|   Académies    |   `r insertion_master_panel |> distinct(Académie) |> nrow()`    |
| Etablissements | `r insertion_master_panel |> distinct(Établissement) |> nrow()` |
|    Domaines    |    `r insertion_master_panel |> distinct(Domaine) |> nrow()`    |
|  Disciplines   |  `r insertion_master_panel |> distinct(Discipline) |> nrow()`   |



Q1: Which fields/specializations lead to the highest wages, have the highest insertion rate, or have the highest level of stable employment?



```{r}
best_specializations_max <- insertion_master_panel |>
  group_by(Académie, Domaine) |>
  summarise(
    MaxSalaire = ifelse(is.na(max(`Salaire brut annuel estimé`, na.rm = TRUE)), "", max(`Salaire brut annuel estimé`, na.rm = TRUE)),
    MaxInsertionRate = ifelse(is.na(max(`Taux d’insertion`, na.rm = TRUE)), "", max(`Taux d’insertion`, na.rm = TRUE)),
    MaxStableEmployment = ifelse(is.na(max(`% emplois stables`, na.rm = TRUE)), "", max(`% emplois stables`, na.rm = TRUE)),
    .groups = "drop"
  ) |>
  arrange(Académie, desc(MaxSalaire), desc(MaxInsertionRate), desc(MaxStableEmployment))
```
**Problem to be solved for the code above**
Value '-Inf' in the column 'MaxInsertionRate' of best_specializations need to be addressed.


```{r}
best_specializations_mean <- insertion_master_panel |>
  group_by(Académie) |>
  summarise(
    MeanSalaire = ifelse(is.na(mean(`Salaire brut annuel estimé`, na.rm = TRUE)), "", mean(`Salaire brut annuel estimé`, na.rm = TRUE)),
    MeanInsertionRate = ifelse(is.na(mean(`Taux d’insertion`, na.rm = TRUE)), "", mean(`Taux d’insertion`, na.rm = TRUE)),
    MeanStableEmployment = ifelse(is.na(mean(`% emplois stables`, na.rm = TRUE)), "", mean(`% emplois stables`, na.rm = TRUE)),
    .groups = "drop"
  ) |>
  arrange(Académie, desc(MeanSalaire), desc(MeanInsertionRate), desc(MeanStableEmployment))

```


NOTE: We could use the aggregate observations for this question, looking at the best paying degree for each year. 




Q2: Is the university that one goes to a significant factor to explain wages? 

We could take one field/specialization taught at different universities, focus on these observations to make a (simple) regression, and try to determine the significance of the "university" factor.

Let's focus on the "Economie" specialization, 30 months after graduation. 

```{r}
reg_econ <- insertion_master_panel |> 
  filter(`Code de la discipline` == "disc03" & situation == "30 mois après le diplôme" & !is.na(`Salaire net médian des emplois à temps plein`))  |> 
  group_by(Établissement) |>
  summarise("Salaire moyen entre 2010 et 2021" = mean(`Salaire net médian des emplois à temps plein`))
```

Note: In order to do the regression, we need to convert the variable Établissement into dummy variable. The followin code is not the final one, I'm still working on it.
```{r}
reg_econ_data <- insertion_master_panel |> 
  filter(`Code de la discipline` == "disc03" & situation == "30 mois après le diplôme" & !is.na(`Salaire net médian des emplois à temps plein`))

reg_econ_data_with_dummies <- reg_econ_data |>
  mutate(Établissement = as.factor(Établissement)) |>
  pivot_wider(names_from = Établissement, values_from = `Salaire net médian des emplois à temps plein`, values_fill = list(`Salaire net médian des emplois à temps plein` = 0))

reference_school <- reg_econ_data_with_dummies |> filter(name == min(name))
reg_econ_data_with_dummies <- reg_econ_data_with_dummies |> filter(name != min(name))

model <- lm(`Salaire net médian des emplois à temps plein` ~ ., data = reg_econ_data_with_dummies)
```




```{r}
insertion_master_panel |>
  group_by(situation) |>
  summarize(moyenne_taux_d_insertion = mean(`Taux d’insertion`, na.rm = TRUE)) |>
  knitr::kable()
```



## Conclusion 



