---
title: "DMC Project: Employment statistics of graduate students"
author: "Lou Delattre and Yufeng Jiang"
format: 
  html: default 
  wordcount-pdf: default 
execute: 
  echo: false
  warning: false
---

```{r}
here::i_am("DM-project-Employment-statistics-of-graduate-student.Rproj")
library(here)
library(vroom)
library(ggplot2)
library(dplyr)
library(tidyr)
library(purrr)
library(knitr)
library(broom)
library(fastDummies)
theme_set(theme_bw())
```

Github repository: <https://github.com/Mapleyf0911/DM-project-Employment-statistics-of-graduate-student.git>

## Goal of our research

We will define the goals of our quantitative analysis. Data on the insertion rate and different measures of wages allow us to compute and make comparisons between sectors, and to emit hypotheses on correlations between some of our variables at various levels. Expressing these hypotheses, we obtain the following questions:

-   Which fields/specializations lead to the highest wages, have the highest insertion rate, or have the highest level of stable employment? This will be the focus of our analysis. We can compute the mean wage/rate for each field and make comparisons.

-   Is the university that one goes to a significant factor to explain wages? We could take one field/specialization taught at different universities, focus on these observations to make a (simple) regression, and try to determine the significance of the "university" factor.

-   How do the wages of these graduates compare to the average national/regional salaries? How do they compare to the average of their respective fields? Using the results of the first question and data from the additional data set, various plot representations could be meaningful.

-   Are there significant differences between observations made 18 months after graduating and observations made 30 months after graduating? It will be necessary to separate the programs where we have 18-month observations, those with 30-month observations, and those with both, and isolate this last category.

-   Do some specializations require to leave the region of the "académie" where the master's degree was done? It could show the concentration of certain industries at national level. 

-   Do some specializations attract more women/scholarship students? There are already studies on the type of profile each field is more likely to attract, thus we can try to find the same results with our data set.

We do not have a unique research question, as it would not allow us to do enough testing at our level, given our data set. However, all of the above-mentioned questions go in the same direction: what can be inferred from our data sets about the situation of graduate students? This will certainly be insufficient to make any real conclusions, nonetheless this may help define guidelines for a bigger project.

## The datasets

### Data import

We aim to analyze the employability, situation of employment and salary of graduate students, depending on their graduate program, university and "académie".

Here, we are using employment statistics from the professional insertion survey of Master students made by the Ministère de l'Enseignement Supérieur et de la Recherche. The survey focus on French graduate students who have completed their initial training ("formation initiale" in French) and have not continued or resumed their studies in the two years following their graduation. The survey shows the employment status at two key time points: 18 months and 30 months after their graduation.

#### Main dataset

```{r}
insertion_master <- vroom(here("data", "fr-esr-insertion_professionnelle-master-national.csv"))
```

|                        |                            |
|------------------------|----------------------------|
| Number of observations | `r NROW(insertion_master)` |
| Number of variables    | `r NCOL(insertion_master)` |

**Source:** <https://data.enseignementsup-recherche.gouv.fr/explore/embed/dataset/fr-esr-insertion_professionnelle-master/table/?disjunctive.academie&disjunctive.numero_de_l_etablissement&sort=-annee>

In this data set, each observation includes:

-   The year of the survey, the type of master's degree, the university number and the "académie" number and name;

-   The name of the university responsible of the degree, the field ("domaine") and subject ("discipline") of the graduate program;<br>

-   The number of responses and response rate;<br>

-   The percentage of women and scholarship students; <br>

-   The "insertion" rate (% of the graduates that are employed);<br>

-   The percentage of students that work full-time, in executive positions, and outside the region of their university;<br>

-   The median monthly net salary and the estimated gross annual salary of graduates that work full time;<br>

-   The regional unemployment rate; <br>

-   First and third quartiles regional net monthly salaries. <br>

#### Complementary data set

For comparison purposes, we found wage data in a report titled "Île-de-France accounts for half of the highest-paid private sector employees in France" of Insee. The data used for this report was collected by the Insee from two databases (Tous Salariés and Flores).<br>

The database Tous Salariés has all the information about employees. They use the administrative declaration submitted by employers. In the private sector, the annual salary salaries and the number of employees data are mainly derived from Nominative Social Declarations ("Déclarations sociales nominatives (DSN)" in French) and Annual Social Data Declaration ("Déclarations annuelles des données sociales (DADS)" in French). Employees in the agricultural sector, employees of private households, apprentices, and interns are excluded from this study.

The database (Flores 2018) covers all employers (civil service, private employers, including individual employers), with the exception of the employment activities of the Ministry of Armed Forces (France). This database can be used to describe salaried employment across all sectors.

From the data set, we have 2018 data on median/average salaries in the Île-de-France region and at national level, taking into account multiple variables such as sector, type of position and gender. We estimate there are enough sectors included in the file to classify all graduate programs.

Source: <https://data.enseignementsup-recherche.gouv.fr/explore/embed/dataset/fr-esr-insertion_professionnelle-master/table/?disjunctive.numero_de_l_etablissement&disjunctive.academie&sort=-salaire_net_median_des_emplois_a_temps_plein&refine.academie=Paris>

This data is presented in several tables. We simply split the file by each table and removed some textual explanatory information before importing the needed table into R.

We have:

-   the different deciles of net wages at the Île-de-France and national levels;

```{r}
Net_wage_EQTP <- vroom(here("data", "Figure_1_Distribution_of_Monthly_Net_Wages_in_Ile-de-France_and_France_EQTP.csv"))
```

-   the percentage of different types of earners in the Île-de-France regions;

```{r}
pct_high_income <- vroom(here("data", "Figure_2_Ile-de-France_Share_in_High_Incomes_High_Wealth_and_High_Wages.csv"))
```

-   the average net wages of each gender in different employment categories;

```{r}
wages_profession_gender <- vroom(here("data", "Figure_4_Average_Monthly_Net_Wages_EQTP_by_Socio-Professional_Category_and_Gender.csv"))
```

|                                         |                                         |
|-----------------------------------------|-----------------------------------------|
| Number of socio-professional categories | `r (NROW(wages_profession_gender)-2)/2` |
| National mean for men                   | `r wages_profession_gender[10,4]`       |
| National mean for women                 | `r wages_profession_gender[10,3]`       |
| IDF mean for men                        | `r wages_profession_gender[5,4]`        |
| IDF mean for women                      | `r wages_profession_gender[5,3]`        |

<small>**Note:** IDF (Île-de-France)</small>

#### Dataset joining

Here, we get the panel data "insertion_master_panel" by joining the wage data from the complementary data set to our main data set.

```{r}
Net_wage_EQTP_wide_regional_national <- Net_wage_EQTP |>
    pivot_wider(names_from = ...1, values_from = c(`ile-de-France`, France), 
              names_sep = " ") 
##
rows_to_fill <- nrow(insertion_master) - nrow(Net_wage_EQTP_wide_regional_national)
##
if (rows_to_fill > 0) {
  repeated_data <- map(1:rows_to_fill, ~ Net_wage_EQTP_wide_regional_national) |>
    bind_rows()
  Net_wage_EQTP_wide_regional_national <- bind_rows(Net_wage_EQTP_wide_regional_national, repeated_data)
}

insertion_master_panel <- cbind(insertion_master, Net_wage_EQTP_wide_regional_national)
```

### Data cleaning

In our main data set, there are 35 variables. Some of them might be superfluous or at least not relevant for our analysis.

-   "Etablissement actuel" (the 5th column) just gives the exact full name of the university, but in reality we know the corresponding university from the abbreviation, so this column is not very helpful to our research and can bu deleted.

-   "cle_ETAB" (the 33th column) could be obtained using more explicit columns. It is redundant.

-   "Id_Paysage" (the 35th column) is redundant. It has the same purpose as "Code de l'établissement".

-   "Taux d'emploi" (the 18th column) and "Taux d'emploi en France" (the 19th column) are missing a significant amount of values (17669 out of 19603 observations). We consider that "Taux d'insertion" is sufficient, as the difference between the employment rate and insertion rate may not be significant. According to the original source, the employment rate is computed including "inactives" (neither working nor in search of employment.) while the insertion rate does not include them.

Therefore, we can delete the 5th, 18th, 19th, 33th and 35th columns in the original dataset.

```{r}
insertion_master_panel <- insertion_master_panel |> select(-c(5, 18, 19, 33, 35))
```


However, some graduate programs have two observations (one after 18 months, one after 30 months). To perfectly identify each observation of each master program, we have to create another variable (or primary key).

-   The identifier is called "obs_ID" and is made of the concatenation of "Annee", "Numéro de l'établissement" and "cle_disc".

```{r}
## création clé 
insertion_master_panel <- insertion_master_panel |>
  mutate(obs_ID = paste(Annee,  `Numéro de l'établissement`, `cle_DISC`, sep = "_"))
```

In the "Remarque" column, there are five possible values for each observation:

1. Université ayant participé à l'enquête mais dont l'effectif est trop petit pour que les résultats soient jugés exploitables;
2. Université ayant participé à l'enquête mais dont le taux de réponse obtenu est insuffisant pour que les résultats soient jugés exploitables;
3. Université dont les résultats sont plus fragiles (taux de réponse inférieur à 50%);
4. Université n'ayant pas participé à l'enquête;
5. N/A (no comment).

Among all observations, only those where the "Remarque" column is either "Université dont les résultats sont plus fragiles (taux de réponse inférieur à 50%)" or "N/A" contain the necessary data for further analysis (e.g., graduate employment rates and salary levels). Therefore, we will retain only those observations that meet these two conditions.

Some of the observations are on gathered data from all degrees of the same discipline, by year. As they are on national data, they are not related to any "académie". We will keep them for analysis purposes but after removing them from the main data set. 

```{r}
## removing 
insertion_master_panel <- insertion_master_panel |> 
  filter(is.na(Remarque)| Remarque == "Université dont les résultats sont plus fragiles (taux de réponse inférieur à 50%)" )

## isolating aggregate observations 
aggregate_data <- insertion_master_panel |> 
  filter(is.na(Académie))

## removing aggregate observations from main dataset 
insertion_master_panel <- insertion_master_panel |> filter(!is.na(Académie))


```

In our data set "insertion_master_panel", many values are missing, due to absence of data ("nd" = non disponible) or unusable data ("ns" = "non significatif" and "fe" = "faible effectif"). Here, we examine how many missing values we have in each column, and address these missing values carefully before our analysis.

```{r}
selected_columns <- insertion_master_panel[, 14:32]

is_non_numeric <- function(x) {
  !is.numeric(suppressWarnings(as.numeric(as.character(x)))) | is.na(x)
}
non_numeric_counts <- sapply(selected_columns, function(column){
  sum(is_non_numeric(column))
})
  
kable(data.frame(non_numeric_counts))
```


```{r}
insertion_master_panel[] <- lapply(insertion_master_panel, function(x) ifelse(x == "ns", NA, x))
insertion_master_panel[] <- lapply(insertion_master_panel, function(x) ifelse(x == "nd", NA, x))
insertion_master_panel[] <- lapply(insertion_master_panel, function(x) ifelse(x == "fe", NA, x))
insertion_master_panel[] <- lapply(insertion_master_panel, function(x) ifelse(x == ".", NA, x))
```

To facilitate our future analysis, we convert some character-formatted data values into numeric format.

```{r}
cols_to_convert <- c(16:21, 23:29)
insertion_master_panel[, cols_to_convert] <- sapply(insertion_master_panel[, cols_to_convert], function(x){
  if (is.character(x)){
    as.numeric(ifelse(is.na(x), NA, x))
  } else {
    x
  }
})
```

## Data analysis


|   Categories   |                             Number                              |
|:---------------------:|:----------------------------------------------:|
|   Académies    |   `r insertion_master_panel |> distinct(Académie) |> nrow()`    |
| Etablissements | `r insertion_master_panel |> distinct(Établissement) |> nrow()` |
|    Domaines    |    `r insertion_master_panel |> distinct(Domaine) |> nrow()`    |
|  Disciplines   |  `r insertion_master_panel |> distinct(Discipline) |> nrow()`   |



### Q1: Which fields/specializations lead to the highest wages, have the highest insertion rate, or have the highest level of stable employment?

```{r}
best_specializations_max <- insertion_master_panel |>
  group_by(Domaine, Discipline) |>
  summarise(
    MaxSalaire = ifelse(all(is.na(`Salaire brut annuel estimé`)), NA_real_, max(`Salaire brut annuel estimé`, na.rm = TRUE)),
    MaxInsertionRate = ifelse(all(is.na(`Taux d’insertion`)), NA_real_, max(`Taux d’insertion`, na.rm = TRUE)),
    MaxStableEmployment = ifelse(all(is.na(`% emplois stables`)), NA_real_, max(`% emplois stables`, na.rm = TRUE)),
    .groups = "drop"
  ) |>
  arrange(Domaine, desc(MaxSalaire), desc(MaxInsertionRate), desc(MaxStableEmployment))
```

For this question, we tried to find the "best fields/specializations" from two perspectives.
We first conducted a preliminary analysis with the optimal level of employment performance in each fields ("Domaine" column). In terms of insertion rate and stable employment rate, the employment performance of graduates from arts, literature and languages fields are the worst, with both rates below 100%, while all other disciplines achieved a 100% employment rate. From the perspective of salary levels, graduates from Law, Economics and Management fields as well as Science, Technology, and Health fields get the highest pay, reaching €49,100. Graduates from arts, literature, and languages fields still performed the worst, with a salary of only €34,300.
```{r}
max_salary_domain <- best_specializations_max |>
  group_by(Domaine) |>
  summarise(MaxSalaire = max(MaxSalaire, na.rm = TRUE)) |>
  arrange(desc(MaxSalaire))

max_insertion_rate_domain <- best_specializations_max |>
  group_by(Domaine) |>
  summarise(MaxInsertionRate = max(MaxInsertionRate, na.rm = TRUE)) |>
  arrange(desc(MaxInsertionRate))

max_stable_employment_domain <- best_specializations_max |>
  group_by(Domaine) |>
  summarise(MaxStableEmployment = max(MaxStableEmployment, na.rm = TRUE)) |>
  arrange(desc(MaxStableEmployment))

merged_domain_stats <- max_salary_domain |>
  left_join(max_insertion_rate_domain, by = "Domaine") |>
  left_join(max_stable_employment_domain, by = "Domaine")

kable(merged_domain_stats, caption = "Optimal Employment Perfomance by Domain")
```

Further, we looked at the average performance of employment in each domain/specialization. We could get the similar conclusion. Graduates from **Sciences, technologies et santé** and **Droit, économie et gestion** fields stand out in terms of average salaries, earning €31,468 and €31,350 respectively, ranking first and second. In contrast, graduates from **Lettres, langues, arts** have the lowest average salary.

Regarding the insertion rate, three fields exceed 90%: **Sciences, technologies et santé**, **Droit, économie et gestion**, and **Masters enseignement**. Among them, **Masters enseignement** excels not only in employment rate but also in stable employment rate, outperforming all other fields in the latter.

Another interesting fact we found is that the average salary for **Masters enseignement** graduates is not as high as in certain other fields, their good performance in both successful employment and employment stability makes it a compelling choice for prospective students.

```{r}
best_domain_mean <- insertion_master_panel |>
  group_by(Domaine) |>
  summarise(
    MeanSalaire = ifelse(all(is.na(`Salaire brut annuel estimé`)), NA_real_, mean(`Salaire brut annuel estimé`, na.rm = TRUE)),
    MeanInsertionRate = ifelse(all(is.na(`Taux d’insertion`)), NA_real_, mean(`Taux d’insertion`, na.rm = TRUE)),
    MeanStableEmployment = ifelse(all(is.na(`% emplois stables`)), NA_real_, mean(`% emplois stables`, na.rm = TRUE)),
    .groups = "drop"
  ) |>
  arrange(desc(MeanSalaire))

kable(best_domain_mean, caption = "Average Employment Perfomance by Domain")

best_domain_long <- best_domain_mean |>
  pivot_longer(
    cols = c(MeanSalaire, MeanInsertionRate, MeanStableEmployment),
    names_to = "Metric",
    values_to = "Value"
  )

best_domain_long <- best_domain_long |>
  mutate(Metric = factor(Metric, levels = c("MeanSalaire", "MeanInsertionRate", "MeanStableEmployment")))
```

```{r}
#| fig-width: 10
#| fig-height: 6

ggplot(best_domain_long, aes(x = Domaine, y = Value, fill = Domaine)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.8) +
  facet_wrap(~ Metric, scales = "free_y") +
  labs(title = "Average Employment Perfomance by Domain",
       x = "Domaine",
       y = "Value",
       fill = "Domaine") +
  theme_minimal() +
  theme(
    legend.position = "right", 
    legend.text = element_text(size = 8), 
    axis.text.x = element_blank(), 
    axis.ticks.x = element_blank(), 
    plot.margin = unit(c(1, 1, 1, 1), "cm") ,
    plot.title = element_text(size = 10, face = "bold", hjust = 0.5)
  ) +
  scale_fill_brewer(palette = "Set2") +
  scale_x_discrete(limits = c("Sciences, technologies et santé", "Droit, économie et gestion", "Masters enseignement", "Sciences humaines et sociales", "Lettres, langues, arts")) 

```


```{r}
best_specializations_mean <- insertion_master_panel |>
  group_by(Discipline, Domaine) |>
  summarise(
    MeanSalaire = ifelse(all(is.na(`Salaire brut annuel estimé`)), NA_real_, mean(`Salaire brut annuel estimé`, na.rm = TRUE)),
    MeanInsertionRate = ifelse(all(is.na(`Taux d’insertion`)), NA_real_, mean(`Taux d’insertion`, na.rm = TRUE)),
    MeanStableEmployment = ifelse(all(is.na(`% emplois stables`)), NA_real_, mean(`% emplois stables`, na.rm = TRUE)),
    .groups = "drop"
  ) |>
  arrange(desc(MeanSalaire))
```


NOTE: We could use the aggregate observations for this question, looking at the best paying degree for each year. 

I don't try the aggregate observations for the Q1, but you can compare the two methods to see if the code above have any necessity to modify. --Yufeng



### Q2: Is the university that one goes to a significant factor to explain wages? 

To explore this question, let's first have a look at the summary of the salary data for economics graduates from different universities. Here, we use the data collected 30 months after graduation.

```{r}
reg_econ <- insertion_master_panel |> 
  filter(`Code de la discipline` == "disc03" & situation == "30 mois après le diplôme" & !is.na(`Salaire net médian des emplois à temps plein`))  |> 
  group_by(Établissement) |>
  summarise("Salaire moyen entre 2010 et 2021" = mean(`Salaire net médian des emplois à temps plein`)) |>
  arrange(desc(`Salaire moyen entre 2010 et 2021`))

top_5 <- reg_econ[1:5, ]
bottom_5 <- reg_econ[(nrow(reg_econ)-4):nrow(reg_econ),]

top_5 <- top_5 |>
  bind_rows(data.frame(`Établissement` = "..."))

merged_table <- top_5 |>
  bind_rows(bottom_5)

merged_table$`Salaire moyen entre 2010 et 2021` <- sapply(merged_table$`Salaire moyen entre 2010 et 2021`, function(x) {
  if (is.na(x)) {
    return(NA) # If the value is NA, keep it as NA
  } else {
    return(format(x, digits = 2, nsmall = 2))  # Keep two decimal places
  }
})

merged_table[is.na(merged_table)] <- "..."

kable(merged_table, align = "c", caption = "Average Salaries of Economics Graduates 30 Months Post-Graduation")
```

  From the table above, we can easily find that there are significant differences in salary levels among economics graduates from different universities. Graduates from Paris-Panthéon-Assas got an average monthly salary of €2,920, while those from Perpignan - Via Domitia earned just over half of that amount. Of course, this is just a rough analysis; there are many other factors that influence the salary levels of graduates in the same field, such as the choice of employment location after graduation. For most industries, the average salary in the region where graduates work has a substantial impact on their income. Therefore, we try to control the effect of other when we do the further analysis in the next part.

===
Note: In order to do the regression, we need to convert the variable Établissement into dummy variable. 

**Regression model**

To analyze the effect of universities on graduate salaries while controlling the effect of other variables, we can construct the following regression model:

$$
Y_i = \beta_0 + \sum_{j=1}^{J-1} \beta_j D_{University_j} + \sum_{k=1}^{K-1} \gamma_k D_{Major_k} + \sum_{l=1}^{L-1} \delta_l D_{City_l} + \phi \cdot Duration + \epsilon_i
$$
Where:<br>
- $D_{University_j}$: Dummy variables for universities.<br>
- $D_{Major_k}$: Dummy variables for majors.<br>
- $D_{City_l}$: Dummy variables for cities.<br>
- $Duration$: Graduation duration (18 or 30 months).<br>

**Data Preparation**

Here, we need to set dummy variables for categorial variables and define reference categories.

```{r}
insertion_master_reg <- insertion_master_panel[, c(1, 4, 6, 8, 11, 20:22, 24)]
ref_group <- aggregate_data[, c(1, 4, 6, 8, 11, 20:22, 24)]

cols_to_convert <- c(6, 7, 9)
ref_group[, cols_to_convert] <- sapply(ref_group[, cols_to_convert], function(x){
  if (is.character(x)){
    as.numeric(ifelse(is.na(x), NA, x))
  } else {
    x
  }
})

insertion_master_reg <- insertion_master_reg |>
  bind_rows(ref_group)
```

```{r}
insertion_master_reg$Académie <-
  as.character(insertion_master_reg$Académie)

insertion_master_reg[is.na(insertion_master_reg[, 3]), 3] <- "Toutes université"
```

```{r}
insertion_master_reg$Établissement <- factor(insertion_master_reg$Établissement)
insertion_master_reg$Domaine <- factor(insertion_master_reg$Domaine)
insertion_master_reg$Académie <- factor(insertion_master_reg$Académie)
insertion_master_reg$situation <- factor(insertion_master_reg$situation)


insertion_master_reg$Établissement <- relevel(insertion_master_reg$Établissement, ref = "Toutes universités et établissements assimilés")
insertion_master_reg$situation <- relevel(insertion_master_reg$situation, ref = "18 mois après le diplôme") 

regression_uni <- lm(`Salaire brut annuel estimé` ~ Établissement + Domaine + situation + `% de diplômés boursiers`, data = insertion_master_reg)
summary(regression_uni)
```

Here, to control the effect of regional salary on the annual salary graduates obtained, we decide to do the regression by different groups of "Académie". However, since in some Académies, there is only one university, it will be impossible to run regression model if we do not remove those Académies. Fortunately, the number of these kind of Académies is small. Removing them out of our dataset would not have a huge impact on our final result.

```{r}
academie_groups <- split(insertion_master_reg, insertion_master_reg$Académie)
lapply(academie_groups, function(insertion_master_reg) {
  sapply(insertion_master_reg[, c("Établissement", "Domaine", "situation")], function(var) {
    length(unique(var))
  })
})
```

```{r}
valid_columns <- sapply(insertion_master_reg[, c("Établissement", "Domaine", "situation")], function(var) {
    length(unique(var)) > 1
  })

```


```{r}

regression_uni_by_group <- lapply(academie_groups, function(insertion_master_reg){
  regression_uni <- lm(`Salaire brut annuel estimé` ~ Établissement + Domaine + situation + `% de diplômés boursiers`, data = insertion_master_reg)
  return(regression_uni)
})

```





### Q3: How do the wages of these graduates compare to the average national/regional salaries? How do they compare to the average of their respective fields?



### Q4: Are there significant differences between observations made 18 months after graduating and observations made 30 months after graduating? It will be necessary to separate the programs where we have 18-month observations, those with 30-month observations, and those with both, and isolate this last category.


```{r}
insertion_master_panel |>
  group_by(situation) |>
  summarize(moyenne_taux_d_insertion = mean(`Taux d’insertion`, na.rm = TRUE)) |>
  knitr::kable()
```



### Q5: Do some specializations require to leave the region of the “académie” where the master’s degree was done? 

```{r}
## The columns '% emplois extérieurs à la région de l'université', '% femmes' and '% de diplômés boursiers' have to be converted into numerical values for Q5 and Q6. 
aggregate_data[, c(22, 26, 27)] <- sapply(aggregate_data[, c(22, 26, 27)], function(x){
  if (is.character(x)){
    as.numeric(ifelse(is.na(x), NA, x))
  } else {
    x
  }
})

aggregate_data |> filter(!is.na(`% emplois extérieurs à la région de l’université`)) |>
  group_by(Domaine) |>
  summarise(`Taux d'employés en dehors de la région` = mean(`% emplois extérieurs à la région de l’université`))
```



```{r}
insertion_master_panel[, c(26, 27)] <- sapply(insertion_master_panel[, c(26, 27)], function(x){
  if (is.character(x)){
    as.numeric(ifelse(is.na(x), NA, x))
  } else {
    x
  }
})

insertion_master_panel |>
  filter(!is.na(`% emplois extérieurs à la région de l’université`)) |>
  group_by(Académie,Domaine) |>
  summarise(`%_ext` = mean(`% emplois extérieurs à la région de l’université`))|>
  slice(which.max(`%_ext`)) |> knitr::kable()
  

```



```{r}
insertion_master_panel |>
  filter(!is.na(`% emplois extérieurs à la région de l’université`)) |>
  group_by(Académie,Domaine) |>
  summarise(`%_ext` = mean(`% emplois extérieurs à la région de l’université`))|>
  slice(which.min(`%_ext`)) |>
    arrange(desc(`%_ext`)) |> knitr::kable()
 
```




-- Pas définitif 
 


### Q6: Do some specializations attract more women/scholarship students ? 


```{r}
## Determining the rounded mean % of women in our survey
average_femme <- round(mean(insertion_master_panel$`% femmes`, na.rm = TRUE), 2)
stdev_femme <- round(sd(insertion_master_panel$`% femmes`, na.rm = TRUE),2)
``` 


In our survey, there is an average `r paste(average_femme)` % of women. We can notice that some specializations have a much higher proportion of women. Keeping only those with a proportion of women higher than the average, we obtain: 

```{r}
## Computing the means over the 11 years 
aggregate_femme <- aggregate_data |>
  filter(!is.na(`% femmes`)) |>
  group_by(Discipline) |>
  summarise(`Taux de femmes` = mean(`% femmes`))

aggregate_femme |> filter(`Taux de femmes` > average_femme) |>
  arrange(desc(`Taux de femmes`) ) |>
  mutate(nb_of_sd = round((`Taux de femmes` - average_femme)/stdev_femme,4)) |> knitr::kable()


```

## Conclusion 


